Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-02-15 Ben_Manuscripts/transport/Outline.tex
Added outline

  \subsection*{Sulfur Analogs}

@@

  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
  near monomer head groups. %BJC: should I give all the solutes nicknames (i.e. their residue names)?
  \begin{itemize}
    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
    \item It can also hydrogen bond with water molecule
    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups so it stays
    close to pore walls.
  \end{itemize}

  Similar rdfs of ethylene glycol and dimercaptoethanol reinforces the lack of influence of hbonding % not really?

  \subsection*{Transport of Ketone-like Solutes}

  The carbonyl group of Acetone is a hydrogen bond acceptor and therefore only
  form hydrogen bonds with water molecules in the pore.

  The hydrophobic character of the two methyl groups on acetone causes the methyl
  groups to gravitate towards the outside of the pore, while the carbonyl group
  reaches towards the pore center in order to hydrogen bond with water molecules.
  \begin{itemize}
	\item Order parameter defined between vector along carbonyl and vector extending
	from acetone COM to pore center is non-zero.
  \end{itemize}

  Acetic acid, since we modeled it solely in its protonated state, has hydrogen
  bond donor and acceptor groups.

  \subsection*{Transport of Ions} % probably just sodium

  Sodium ions also exhibit hop diffusion because polarized water and
  carboxylate head groups both work to neutralize its charge.
  \begin{itemize}
	\item Ions get trapped in oxygen 'cages' composed of combinations
	of water molecules, carboxylate head groups and ether oxygens connecting
	the head groups to their tails.
  	\item Interesting coordination number data
	\item Dwell time proportional to surrounding charge within coordination shell
  \end{itemize}

  \subsubsection*{Remarks}

  Overwhelming amount of water in 10 wt\% system makes hydrogen bonding
  competitive between head groups and water.
  %MRS: not sure what you mean above.

  \subsection{Design Suggestions}

>>>>

  \subsection*{Transport of Thiols} % BJC: maybe put this after next section and call it sulfur analogs and include DMSO?

@@

  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
  near monomer head groups. %BJC: should I give all the solutes nicknames (i.e. their residue names)?
  \begin{itemize}
    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
    \item It also hydrogen bond with water molecules which causes it to stay in the pore region
    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups so it stays
    close to pore walls.
  \end{itemize}

  \subsection*{Transport of Ketones}

  %BJC: DMSO might be added to this section. 
  %BJC: DMSO might be slow because it's miscible in organic and polar solvents

  The 4 ketone-like molecules tested show a range of transport behaviors.
  \begin{itemize}
    \item Urea, Acetic Acid, Acetamide and Acetone are all characterized by a carbonyl group
    with two attached heavy atoms. 
    \item All have approximately the same molecular weight and are planar molecules due to
    the sp2 hybridization of the carbonyl group.
    \item The fastest solute of this grouping, Urea, has an MSD comparable to that of ethylene
    glycol while the slowest, Acetone, has an MSD one third of that of Urea.
  \end{itemize}

  Once again, the trends in the MSD can in large part be explained by the solutes'
  ability to hydrogen bond.  % or maybe just polarity
  \begin{itemize}
  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
  	while acetone is the first instance of a molecule in this study that can only
  	accept hydrogen bonds.
  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
  	its density is high near the pore center, particularly near the monomer head groups.
  	\item Acetamide has only one nitrogen atom. One of two peaks in its density is 
  	located close to the peak of Urea, likely corresponding to hydrogen bonds with head groups.
  	A second peak is located within the head group region. %BJC: hbonds with ethers vs. head groups. Or is it just planarity?
  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
  	a peak close to the carboxylate groups.  %BJC: hbonds with 
  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
    its low polarity and planar shape gives it comparable stability when trapped between head groups.
%  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
%  	other is relatively deep in the head group region.
  \end{itemize}

  \subsection*{Hydrogen bond acceptors}  % Need a better heading since all molecules in this study are acceptors

  The final set of molecules we studied can accept hydrogen bonds, but cannot donate
  them. 
  \begin{itemize}
  	\item Among this set are the two slowest solutes in our study: Tetrahydrofuran and Dimethyl Formamide.
  	\item Ethyl acetate and Propylene Carbonate are only marginally faster, however they
  	are both larger molecules. %BJC: not sure how far I should dive into this point
  \end{itemize}

  The radial density functions highlight the solutes' preference for the 
  pore region.
  \begin{itemize}
  	\item There are small peaks in the radial density greater than 1 nm 
  	from the pore center.
  	\item The solutes become trapped in these regions where each step is
  	highly anti-correlated to its previous step, leading to very low MSDs.
  	\item The large size and nonplanar shapes of ethyl acetate and propylene 
  	carbonate may destabilize entrapment in the tail region more quickly, leading
  	to slightly faster transport. 
%  	\item The relatively small amount of movement on the timescales studied 
%  	do not reveal definitive reasons
  	\item Overall, 
  \end{itemize}
  Ethyl acetate spends all of its time in a linear or near-linear conformation. % can show with dihedrals

  THF and DMF are both planar which allows them to

  % THF shows highly anticorrelated hops

  %All have comparable densities near pore center except acetone which is lower

%  \subsection*{Transport of Ions} % probably just sodium
%
%  Sodium ions also exhibit hop diffusion because polarized water and
%  carboxylate head groups both work to neutralize its charge.
%  \begin{itemize}
%	\item Ions get trapped in oxygen 'cages' composed of combinations
%	of water molecules, carboxylate head groups and ether oxygens connecting
%	the head groups to their tails.
%  	\item Interesting coordination number data
%	\item Dwell time proportional to surrounding charge within coordination shell
%  \end{itemize}

  \subsection{Design Principles}
